%% Abderrahmane El Bissari — Flutter Developer CV
%% Tailored for Agh Data Agency — QA Testeur Mobile (Flutter & Django)
%% Paste into Overleaf (pdflatex)

\documentclass[10pt, a4paper]{article}

% ─── Packages ───────────────────────────────────────────────────────────────
\usepackage[a4paper, top=1.8cm, bottom=1.8cm, left=2cm, right=2cm]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{multicol}

% ─── Colors ─────────────────────────────────────────────────────────────────
\definecolor{black}{HTML}{111111}
\definecolor{darkgray}{HTML}{333333}
\definecolor{medgray}{HTML}{555555}
\definecolor{lightgray}{HTML}{AAAAAA}
\definecolor{rulecol}{HTML}{111111}

% ─── Hyperlinks ─────────────────────────────────────────────────────────────
\hypersetup{colorlinks=false, hidelinks}

% ─── Typography ─────────────────────────────────────────────────────────────
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ─── Section Titles ──────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{black}}
  {}{0pt}
  {}
  [\vspace{1pt}\color{rulecol}\titlerule\vspace{4pt}]

\titlespacing{\section}{0pt}{10pt}{4pt}

% ─── Custom commands ─────────────────────────────────────────────────────────
\newcommand{\cvheader}[4]{%
  \begin{center}
    {\Huge\bfseries\color{black} #1}\\[4pt]
    {\small\color{medgray} #2 \quad|\quad #3 \quad|\quad #4}
  \end{center}
}

\newcommand{\entry}[4]{%
  \textbf{\color{black}#1} \hfill \textit{\small\color{medgray}#2}\\
  \textit{\small\color{darkgray}#3} \hfill \textit{\small\color{lightgray}#4}\\
}

\newcommand{\project}[3]{%
  \textbf{\color{black}#1} \hfill \textit{\small\color{medgray}#2}\\
  {\small\color{darkgray}#3}\\
}

\newcommand{\skillrow}[2]{%
  \textbf{\small #1:} & {\small\color{darkgray} #2}\\[2pt]
}

% ─── List style ──────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt,
  label={\small$\bullet$}
}

% ═════════════════════════════════════════════════════════════════════════════
\begin{document}

% ─── HEADER ──────────────────────────────────────────────────────────────────
\cvheader{Abderrahmane El Bissari}%
  {\href{mailto:abdo.bissari@gmail.com}{abdo.bissari@gmail.com}}%
  {+212 706 313 526}%
  {Marrakech, Morocco — Remote}

\vspace{6pt}

% ─── PROFILE ─────────────────────────────────────────────────────────────────
\section{Profile}

Flutter Developer with hands-on professional experience building cross-platform 
mobile applications (iOS/Android), now targeting QA \& software quality roles. 
Strong foundation in \textbf{Python} and \textbf{C} (through rigorous systems 
programming at \textbf{1337 — UM6P}), with active exploration of \textbf{AI and 
LLM-based tools} in development workflows. Familiar with \textbf{REST API} 
design and consumption, \textbf{Firebase} ecosystem, and backend integration — 
providing a solid base for understanding and testing Django-backed APIs. 
Detail-oriented, analytical, and fully remote-ready.

% ─── EXPERIENCE ──────────────────────────────────────────────────────────────
\section{Experience}

\entry{WordPress \& Flutter Developer}{June 2025 – August 2025}%
      {M5Tech Company}{Marrakech, Morocco}
\begin{itemize}
  \item Designed and shipped a full client project: Flutter mobile app + WordPress web platform.
  \item Validated REST API integration end-to-end, identifying and reporting integration issues between frontend and backend layers.
  \item Ensured smooth cross-platform performance on iOS and Android; flagged and tracked UI/UX regressions during iterative releases.
  \item Collaborated with designers and backend engineers following Agile/Scrum methodologies.
\end{itemize}

\vspace{6pt}

\entry{Flutter \& Web Developer — Internship}{April 2025 – May 2025}%
      {M5Tech Company}{Marrakech, Morocco}
\begin{itemize}
  \item Led Flutter app development with Node.js backend integration and REST API consumption.
  \item Manually tested API endpoints using Postman; documented discrepancies between expected and actual responses.
  \item Delivered production-ready modules with clear UI/logic/data separation, enabling easier regression testing.
\end{itemize}

% ─── 1337 PROJECTS ───────────────────────────────────────────────────────────
\section{1337 School Projects (Systems \& Low-Level Programming)}

\project{Libft}{2024}%
  {Re-implementation of the C standard library from scratch. Deepened understanding of memory management, pointers, and safe string/data manipulation — foundational for writing and testing reliable low-level code.}

\vspace{4pt}
\project{get\_next\_line}{2024}%
  {Custom implementation of a line-by-line file reader in C using static variables and dynamic memory. Exercised edge-case thinking: EOF handling, empty files, multi-fd reading — directly applicable to systematic test case design.}

\vspace{4pt}
\project{ft\_printf}{2024}%
  {Full reimplementation of the \texttt{printf} function in C, handling multiple format specifiers and edge cases. Developed rigorous input/output validation habits essential for QA work.}

\vspace{4pt}
\project{Born2beroot}{2024}%
  {System administration project: configured a Debian virtual machine with strict security policies (SSH hardening, UFW firewall, sudo rules, password policies). Introduced to environment setup, monitoring, and compliance verification.}

\vspace{4pt}
\project{push\_swap}{2025}%
  {Sorting algorithm challenge in C: sort a stack of integers using a limited instruction set with minimum operations. Sharpened algorithmic thinking, performance analysis, and behaviour verification under constraints.}

\vspace{4pt}
\project{A-Maze-ing}{2025}%
  {Maze generation and solving project. Implemented and validated pathfinding logic, testing correctness across varied maze configurations and boundary conditions.}

\vspace{4pt}
\project{Codexion}{2025}%
  {Advanced project combining systems-level C programming with higher-level tooling. Explored integration between components and practiced structured debugging and validation of complex multi-module behavior.}

% ─── FLUTTER PROJECTS ────────────────────────────────────────────────────────
\section{Mobile Projects}

\project{AquaManage}{2025}%
  {Water consumption \& billing management app. Flutter + MVVM + Cubit + local API. Tested API data flows and UI state transitions across feature modules.}

\vspace{4pt}
\project{PDF Quizzer}{2025}%
  {App converting PDF content into MCQ / True-or-False quizzes. Flutter + Dart, dynamic question generation. Validated parsing accuracy and UI rendering across various PDF formats.}

\vspace{4pt}
\project{Tut App}{2024}%
  {Modular Flutter app built with Clean Architecture and full REST API integration. Tested endpoint contracts and verified UI behaviour against API responses.}

% ─── TECHNICAL SKILLS ────────────────────────────────────────────────────────
\section{Technical Skills}

\begin{tabular}{@{}p{3.2cm} p{13cm}@{}}
  \skillrow{Mobile}{Flutter, Dart — cross-platform iOS/Android, UI testing, performance debugging}
  \skillrow{Languages}{Python (advanced), C (advanced), Dart, JavaScript, TypeScript, PHP, SQL, HTML/CSS}
  \skillrow{AI / LLM}{Actively exploring LLM-based development tools (prompt engineering, AI-assisted coding, model integration); GitHub Copilot, Windsurf, Cursor}
  \skillrow{Backend \& APIs}{REST API design \& consumption, Firebase (Auth, Firestore, FCM, Storage), Node.js — solid base for understanding Django API structures}
  \skillrow{QA \& Testing}{Manual functional testing, API testing (Postman), bug documentation, regression verification, Firebase Crashlytics}
  \skillrow{Project Tools}{Git, GitHub, Jira/Trello (familiar), Firebase Console, VS Code, Android Studio}
  \skillrow{Practices}{Agile/Scrum, clean code, OOP, Web Security (SQLi, XSS), systematic debugging}
\end{tabular}

% ─── EDUCATION ───────────────────────────────────────────────────────────────
\section{Education}

\entry{1337 Coding School — UM6P}{2025 – Present}%
      {Software Engineering Program (C, Python, Systems, Algorithms)}{Rabat, Morocco}

\vspace{4pt}
\entry{ISTA NTIC Sidi Youssef Ben Ali}{2023 – 2025}%
      {Diploma in Mobile Applications Development — \textbf{High Honors}}{Marrakech, Morocco}

\vspace{4pt}
\entry{Lyc\'ee Hassan II}{2022 – 2023}%
      {Scientific Baccalaureate (SVT) — \textbf{Honors}}{Marrakech, Morocco}

% ─── LANGUAGES ───────────────────────────────────────────────────────────────
\section{Languages}

\begin{tabular}{@{}lll@{}}
  \textbf{Arabic} — Native \quad &
  \textbf{English} — Professional working proficiency \quad &
  \textbf{French} — Intermediate (technical reading)
\end{tabular}

% ─── SOFT SKILLS ─────────────────────────────────────────────────────────────
\section{Soft Skills}

\begin{multicols}{2}
\begin{itemize}
  \item Autonomous \& self-managed (100\% remote ready)
  \item Analytical mindset, sharp eye for detail
  \item Patient and methodical in bug investigation
  \item Clear written communication for bug reports
  \item Collaborative with mobile and backend teams
  \item Fast learner, curiosity-driven
\end{itemize}
\end{multicols}

\end{document}